### 2025-11-06 modern-portfolio-theory.qmd
20251106 - typo

ggplot2::ggplot(
  data = team_projections2,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel() +
  labs(
    x = "Standard Deviation of Players' Fantasy Points From Week-to-Week",
    y = "Mean of Players' Fantasy Points Across Weeks",
    title = "Mean vs Standard Deviation of Players' Projected Fantasy Points"
  ) +
  theme_classic()
```

>>>>

ggplot2::ggplot(
  data = team_projections2,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel() +
  labs(
    x = "Standard Deviation of Players' Fantasy Points From Week-to-Week",
    y = "Mean of Players' Fantasy Points Across Weeks",
    title = "Mean vs Standard Deviation of Players' Actual Fantasy Points"
  ) +
  theme_classic()
```
